\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
\begin{list}{\ding{113}}{%
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} \setlength{\parskip}{0in}
\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
\begin{list}{$\bullet$}{%
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} \setlength{\parskip}{0in}
\setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{hyperref}
\usepackage{color}

\begin{document}

\name{Haitao Yuan \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.2in}p{4in}}
Ph.D.             & {Tel:}  (1)xxx-220-xxxx or (86)18813119708\\            
Department of Electrical and Computer Engineering   & {E-mail:}  haitao.yuan@njit.edu \\
New Jersey Institute of Technology & {\href{https://scholar.google.com.hk/citations?user=ifV9ph4AAAAJ\&hl=en}{Google Scholar}}\\
University Heights, Newark, NJ, 07102  & \\
\end{tabular}

\section{\sc Research Interests}
Cloud computing, data center, green computing, energy optimization, performance modeling and analysis, meta-heuristic optimization algorithms

\section{\sc Education}
{\bf New Jersey Institute of Technology}, Newark, New Jersey USA\\
%{\em Department of Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Computer Engineering, \hfill{01/2019--08/2020}
\begin{itemize}
\item Dissertation Title: ``Energy and Performance-optimized Scheduling Methods for Tasks in Distributed Cloud and Edge Computing Systems''
\item Advisor:  \textbf{Prof. MengChu Zhou}, Distinguished Professor, IEEE Fellow
\end{itemize}
\end{list1}

{\bf Beihang University}, Beijing, China\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Modeling Simulation Theory and Technology, \hfill{09/2012--07/2016}
\begin{itemize}
\item Dissertation Title: ``Researches on Request Scheduling and Resouce Allocation in Cloud Data Centers''
\item Advisor:  \textbf{Prof. Bo Hu Li}, Academician, Chinese Academy of Engineering
\end{itemize}
\end{list1}

{\bf Northeastern University}, Shenyang, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] M.E., Software Engineering, \hfill{09/2010--07/2012}
\end{list1}

{\bf Northeastern University}, Shenyang, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.E., Software Engineering, \hfill{08/2006--07/2010}
\end{list1}

\section{\sc Academic Experience}
{\bf New Jersey Institute of Technology}, Newark, New Jersey USA\\
\vspace*{-.1in}
\begin{list1}
	\item[] Ph.D. Candidate, Department of Electrical and Computer Engineering, \hfill{01/2019--08/2020}
%	\item[] Includes current Ph.D.~research, Ph.D. level coursework and research projects.
	\item[] Advisor:  \textbf{Prof. MengChu Zhou}, Distinguished Professor, IEEE Fellow
\end{list1}

{\bf Beijing Jiaotong University}, Beijing, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] \textbf{Associate Professor}, Software Engineering, \hfill{11/2018--12/2018}
\end{list1}

{\bf Beijing Jiaotong University}, Beijing, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] \textbf{Assistant Professor}, Software Engineering, \hfill{05/2016--10/2018}
\end{list1}

{\bf New Jersey Institute of Technology}, Newark, New Jersey USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] \textbf{Visiting Scholar}, Software Engineering, \hfill{12/2017--11/2018}
\item[] Advisor:  \textbf{Prof. MengChu Zhou}, Distinguished Professor, IEEE Fellow
\end{list1}

{\bf New Jersey Institute of Technology}, Newark, New Jersey USA\\
\vspace*{-.1in}
\begin{list1}
\item[] Visiting Ph.D. Student, Department of Electrical and Computer Engineering, \hfill{10/2015-01/2016}
\item[] Advisor:  \textbf{Prof. MengChu Zhou}, Distinguished Professor, IEEE Fellow
\end{list1}

{\bf City University of Hong Kong}, Kowloon, Hong Kong\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Student, Department of Computer Science, \hfill{08/2013-02/2014}
\item[] Advisor:  \textbf{Prof. Xiaohua Jia}, Chair Professor, IEEE Fellow
\end{list1}

\section{\sc Research and development grants}
\begin{enumerate}
	%	\item NSF NeTS: Small: Free Space Optics as Backhaul and Energizer for Drone-assisted
	%	Networking, NSF CNS-1814748, PI: Dr. Nirwan Ansari, 2018-Present.
	%	\item NSF NeTS: Small: Free Space Optics as Backhaul and Energizer for Drone-assisted Networking, NSF CNS-1814748, PI: Dr. Nirwan Ansari, 2018-Present.
	%	\item Improving Energy Reliability by Co-Optimization Planning for Interdependent Electricity and Natural Gas Infrastructure Systems, NSF, CMMI1635339, \textbf{\$203,616} (\textbf{\$203,616}), \textbf{Single PI}.
	\item Big Data-driven Method for Intelligent Scheduling and Resource Optimization of Deep Space-time Sensitive Cloud Workflow, National Natural Science Foundation of China, 61802015, 01/2019--12/2021, \textbf{270,000 RMB}, \textbf{PI}
	\item Parallel Big Data Analysis and Deep Learning Model Construction in Water Environment, Beijing Jiaotong University, R19L00150, 11/2019--12/2020, \textbf{210,000 RMB}, \textbf{PI}
	\item Data Feature Extraction Method and Software Implementation for Complex System Simulation, Beijing Jiaotong University, R19L00070, 04/2019--12/2021, \textbf{220,000 RMB}, \textbf{PI}
	\item Design and Software Implementation of Intent Recognition Model Based on Stack Autoencoder, Beijing Jiaotong University, R19L00060, 04/2019--12/2021, \textbf{130,000 RMB}, \textbf{PI}
	\item Task Scheduling Algorithm for Space-time Awareness of Green Cloud Computing System, Beijing Jiaotong University, 2019JBM072, 04/2019--03/2021, \textbf{25,000 RMB}, \textbf{PI}
	\item Dynamic Allocation and Optimization of Non-steady-state Hybrid Computing Resources Based on SDN, China Post-Doctoral Science Foundation, 2017T100034, 06/2017--12/2018, \textbf{150,000 RMB}, \textbf{PI}
	\item Research on Time-sensitive Hybrid Request Scheduling and Optimization Methods for Cloud Data Centers, China Post-Doctoral Science Foundation, 2016M600912, 01/2017--04/2018, \textbf{50,000 RMB}, \textbf{PI}
	\item Research on Time-aware Request Scheduling Method in Hybrid Cloud, Beijing Jiaotong University, 2016RC030, 07/2016--07/2018, \textbf{100,000 RMB}, \textbf{PI}
\end{enumerate}

\section{\sc Patents}
{\bf U.S. Patents}
\begin{enumerate}
	\item Ahmed Chiheb Ammari, \textbf{Haitao Yuan}, Jing Bi, MengChu Zhou, Yusuf Al-Turki and Abdullah Abusorrah, ``Temporal Task Scheduling in a Hybrid System", U.S. Patent No. 10528396, Issued Date: 01/07/2020.
\end{enumerate}

{\bf Chinese Patents}
\begin{enumerate}
	\item \textbf{Haitao Yuan}, Jing Bi and Libo Zhang, Load-aware Request Routing Method in SDN-based Cloud Data Center, Patent No. CN106850726 B, Issued Date: 11/15/2019.
	\item \textbf{Haitao Yuan} and Jing Bi, Revenue-based Request Access Control Method in Distributed Multi-cloud Data Center, Patent No. 2016104567265.
	\item \textbf{Haitao Yuan}, Adaptive Multi-objective Hybrid Differential Evolution Algorithm Based on Simulated Annealing and Information Entropy, Patent No. 2019105016329.
	\item \textbf{Haitao Yuan}, Spatio-temporal Sensitive Task Scheduling and Optimization Method in Distributed Remote Multiple Cloud Data Centers, Patent No. 201811054497X.
	\item \textbf{Haitao Yuan}, Profit and Performance Sensitive Multi-objective Task Scheduling Method for Distributed Green Cloud Data Center, Patent No. 2018111885539.
	\item \textbf{Haitao Yuan} and Nan Ying, Heuristic Request Scheduling Method for Delay-sensitive Applications in Multiple Cloud Data Centers, Patent No. 201711180352X.
	\item \textbf{Haitao Yuan}, Space-aware Request Scheduling and Optimization Method in Distributed Green Cloud Data Centers, Patent No. CN108123995B, Issued Date: 02/21/2020.
	\item \textbf{Haitao Yuan}, Execution Time Prediction Method of Simulation Requests Based on Deep Fuzzy Stack Autoencoder, Patent No. 2017110684330.
	\item \textbf{Haitao Yuan}, Profit-sensitive Task Scheduling Method for Complex Simulation Workflow Applications, Patent No. 2017110407075.
\end{enumerate}

\section{\sc Publications}

{\bf {Book Chapters}}
\begin{enumerate}
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Spatio-Temporal Multi-Application Request Scheduling in Energy-Efficient Data Centers," \emph{Energy Efficient Computing \& Electronics: Devices to Systems}, CRC Press, Taylor \& Francis Group, 2019.
\end{enumerate}

%{\bf Journal Articles: (*Corresponding author)}
{\bf {Refereed Journal Articles: ($^{*}$Corresponding author)}}
\begin{enumerate}
\item \textbf{Haitao Yuan} and MengChu Zhou, ``Profit-maximized Collaborative Computation Offloading and Resource Allocation in Distributed Cloud and Edge Computing Systems," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--12, 03/7/2020, Submitted. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, MengChu Zhou and Qing Liu, ``Fine-grained and Arbitrary Task Scheduling for Heterogeneous Applications in Distributed Green Clouds," \emph{IEEE/CAA Journal of Automatica Sinica}, pp. 1--13, 01/23/2020, DOI: 10.1109/JAS.2020.1003177, Online, May 2020.
\item \textbf{Haitao Yuan} and MengChu Zhou, ``Energy-consumption and Performance-optimized Task Scheduling in Distributed Data Centers," \emph{IEEE Transactions on Systems, Man and Cybernetics: Systems}, pp. 1--10, 11/03/2020, Submitted. (\textbf{SCI, Q1, IF 7.351})
\item \textbf{Haitao Yuan} and MengChu Zhou, ``Energy-efficient and QoS-optimized Adaptive Task Scheduling and Management in Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--12, 05/07/2020, Submitted. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Geography-Aware Task Scheduling for Profit Maximization in Distributed Green Data Centers," \emph{IEEE Transactions on Cloud Computing}, pp. 1--11, 04/11/2019, Submitted. (\textbf{SCI, Q1, IF 5.967})
\item \textbf{Haitao Yuan}, Jing Bi, MengChu Zhou, Qing Liu and Ahmed Ammari, ``Bi-objective Task Scheduling for Distributed Green Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--12, 12/07/2019, DOI: 10.1109/TASE.2019.2958979. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Heng Liu, Jing Bi and MengChu Zhou, ``Revenue and Energy Cost-Optimized Biobjective Task Scheduling for Green Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--14, 01/16/2020, DOI: 10.1109/TASE.2020.2971512. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Profit-Sensitive Spatial Scheduling of Multi-Application Tasks in Distributed Green Clouds," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--10, 05/08/2019, DOI: 10.1109/TASE.2019.2909866. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Multiqueue Scheduling of Heterogeneous Tasks With Bounded Response Time in Hybrid Green IaaS Clouds," \emph{IEEE Transactions on Industrial Informatics}, vol. 15, no. 10, pp. 5404--5412, Oct. 2019. DOI: 10.1109/TII.2019.2901518. (\textbf{SCI, Q1, IF 7.377})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Spatiotemporal Task Scheduling for Heterogeneous Delay-Tolerant Applications in Distributed Green Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 16, no. 4, pp. 1686--1697, Oct. 2019. DOI: 10.1109/TASE.2019.2892480. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Temporal Task Scheduling of Multiple Delay-Constrained Applications in Green Hybrid Cloud," \emph{IEEE Transactions on Services Computing}. DOI: 10.1109/TSC.2018.2878561. (\textbf{SCI, Q1, IF 5.707})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Spatial Task Scheduling for Cost Minimization in Distributed Green Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 16, no. 2, pp. 729--740, Apr. 2019. DOI: 10.1109/TASE.2018.2857206. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi, MengChu Zhou and Khaled Sedraoui, "WARM: Workload-Aware Multi-Application Task Scheduling for Revenue Maximization in SDN-Based Cloud Data Center," \emph{IEEE Access}, vol. 6, pp. 645--657, 2018. DOI: 10.1109/ACCESS.2017.2773645. (\textbf{SCI, Q1, IF 4.098})
\item \textbf{Haitao Yuan}, Jing Bi, MengChu Zhou and A. C. Ammari, "Time-Aware Multi-Application Task Scheduling With Guaranteed Delay Constraints in Green Data Center," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 15, no. 3, pp. 1138--1151, Jul. 2018. DOI: 10.1109/TASE.2017.2741965. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi, Wei Tan, MengChu Zhou, Bo Hu Li and Jianqiang Li. ``TTSA: An Effective Scheduling Approach for Delay Bounded Tasks in Hybrid Clouds," \emph{IEEE Transactions on Cybernetics}, vol. 47, no. 11, pp. 3658--3668, Nov. 2017. DOI:10.1109/TCYB.2016.2574766. (\textbf{SCI, Q1, IF 10.387})
\item \textbf{Haitao Yuan}, Jing Bi, Wei Tan and Bo Hu Li. ``Temporal Task Scheduling with Constrained Service Delay for Profit Maximization in Hybrid Cloud," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 14, no. 1, pp. 337-348, Jan. 2017. DOI:10.1109/TAS E.2016.2526781. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi, Wei Tan and Bo Hu Li. ``CAWSAC: Cost-Aware Workload Scheduling and Admission Control for Distributed Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 13, no. 2, pp. 976--985, Apr. 2016. DOI:10.1109/TASE.2015 .2427234. (\textbf{SCI, Q1, IF 5.524})
\item \textbf{Haitao Yuan}, Jing Bi and Bo Hu Li. ``Workload-Aware Request Routing in Cloud Data Center Using Software-Defined Networking," \emph{Journal of Systems Engineering and Electronics}, vol. 26, no. 1, pp.151--160, Feb. 2015. DOI:10.1109/JSEE.2015.00020. (\textbf{SCI, Q4, IF 0.721})
\item \textbf{Haitao Yuan}, Jing Bi, Bo Hu Li and Wei Tan. ``Cost-Aware Request Routing in Multi-Geography Cloud Data Centers Using Software-Defined Networking," \emph{Enterprise Information Systems}, vol. 11, no. 3, pp. 359--388, Jun. 2015. DOI:10.1080/17517575.2015.1048833. (\textbf{SCI, Q2, IF 2.122})
\item Jing Bi, Heng Liu, \textbf{Haitao Yuan} and MengChu Zhou, ``Energy-aware and Bi-objective Scheduling of Green Cloud Tasks," \emph{IEEE Transactions on Systems, Man and Cybernetics: Systems}, pp. 1--11, 01/27/2020, Submitted. (\textbf{SCI, Q1, IF 7.351})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$} and MengChu Zhou, ``Large-Scale Water Quality Prediction with Integrated Deep Neural Network," \emph{IEEE Transactions on Systems, Man and Cybernetics: Systems}, pp. 1--11, 02/26/2020, Major revision. (\textbf{SCI, Q1, IF 7.351})
\item Yang Fu, Zeyu Zheng, MengChu Zhou, \textbf{Haitao Yuan$^{*}$} and Xiwang Guo, ``New Results on Joint Classification of Vertical Structure of Ocean Properties at a Global Scale," \emph{IEEE Access}, pp. 1--8, 03/24/2020, DOI: 10.1109/ACCESS.2020.2985527. (\textbf{SCI, Q1, IF 4.098})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$}, MengChu Zhou, Jia Zhang and Qing Liu, ``ARIMA-Based Multi-Application Workload Prediction with Wavelet Decomposition and Savitzky-Golay Filter in Clouds," \emph{IEEE Transactions on Systems, Man and Cybernetics: Systems}, pp. 1--10, 09/14/2019, Submitted. (\textbf{SCI, Q1, IF 7.351})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$}, Shuang Li, MengChu Zhou and Jia Zhang, ``Time-aware and Short-term Task Prediction with a Deep Learning Approach in Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--11, 03/02/2020, Submitted. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, Shuang Li, \textbf{Haitao Yuan$^{*}$} and MengChu Zhou, ``BG-LSTM: Integrated Deep Learning Method for Workload and Resource Prediction in Cloud Computing Systems," \emph{IEEE Transactions on Automation Science and Engineering}, pp. 1--9, 03/04/2020, Submitted. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$} and MengChu Zhou, ``Temporal Prediction of Multiapplication Consolidated Workloads in Distributed Clouds," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 16, no. 4, pp. 1763--1773, Oct. 2019. DOI: 10.1109/TASE.2019.2895801. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, \textbf{Haitao Yuan}, Libo Zhang and Jia Zhang, ``SGW-SCN: An Integrated Machine Learning Approach for Workload Forecasting in Geo-distributed Cloud Data Centers," \emph{Information Sciences}, vol. 481, pp. 57--68, May 2019. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$} and Wei Tan, ``Deadlock Prevention for Service Orchestration via Controlled Petri Nets," \emph{Journal of Parallel and Distributed Computing}, vol. 124, pp. 92--105, Feb. 2019. (\textbf{SCI, Q2, IF 1.189})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$} and MengChu Zhou, ``A Petri Net Method for Compatibility Enforcement to Support Service Choreography," \emph{IEEE Access}, vol. 4, pp. 8581--8592, Sep. 2016. (SCI, Q1, IF 4.098)
\item Jing Bi, \textbf{Haitao Yuan$^{*}$}, Wei Tan and Bo Hu Li, ``TRS: Temporal Request Scheduling with Bounded Delay Assurance in a Green Cloud Data Center," \emph{Information Sciences}, vol. 360, pp. 57--72, Sept. 2016. DOI: 10.1109/ACCESS.2016.2614325. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$}, Ming Tie and Xiao Song, ``Heuristic Virtual Machine Allocation for Multi-tier Ambient Assisted Living Applications in a Cloud Data Center," \emph{China Communications}, vol. 13, no. 5, pp. 56--65, May 2016. DOI: 10.1109/CC.2016.7489974. (\textbf{SCI, Q2, IF 1.514})
\item Jing Bi, \textbf{Haitao Yuan$^{*}$}, \textit{et al.}, ``Application-Aware Dynamic Fine-Grained Resource Provisioning for Virtualized Cloud Data Centers," \emph{IEEE Transactions on Automation Science and Engineering}, vol. 14, no. 2, pp. 1172--1184, Apr. 2017. DOI: 10.1109/TASE.2015.2503325. (\textbf{SCI, Q1, IF 5.524})
\item Jing Bi, \textbf{Haitao Yuan}, Ming Tie and Wei Tan, ``SLA-Based Optimisation of Virtualised Resource for Multi-tier Web Applications in Cloud Data Centres," \emph{Enterprise Information Systems}, vol. 9, no. 7, pp. 743--767, Jun. 2015. (\textbf{SCI, Q2, IF 2.122})
\item Jing Bi, \textbf{Haitao Yuan}, MengChu Zhou and Qing Liu, ``Time-Dependent Cloud Workload Forecasting via Multi-Task Learning," \emph{IEEE Robotics and Automation Letters}, vol. 4, no. 3, pp. 2401--2406, Jul. 2019. DOI: 10.1109/LRA.2019.2899224. (\textbf{EI})
\item Jing Bi, Tianzhi Feng and \textbf{Haitao Yuan$^{*}$}, ``Real-time and Short-term Anomaly Detection for GWAC Light Curves," \emph{Computers in Industry}, vol. 97, pp. 76--84, May 2018. (\textbf{SCI, Q1, IF 4.769})
\item Qingfeng Yao, Zeyu Zheng, Liang Qi, \textbf{Haitao Yuan}, Xiwang Guo, Ming Zhao, Zhi Liu and Tianji Yang, ``Path Planning Method with Improved Artificial Potential Field--A Reinforcement Learning Perspective," \emph{IEEE Access}, pp. 1--9, 05/03/2020, Submitted. (\textbf{SCI, Q1, IF 4.098})
\item Jing Bi, Tianzhi Feng, \textbf{Haitao Yuan} and Zhen Wei, ``Time-aware Efficient Prediction and Anomaly Detection for Large-scale Light Curves," \emph{International Journal of Machine Intelligence and Sensory Signal Processing}, vol. 2, no. 2, pp. 173--188, Jul. 2018. (\textbf{EI})
\end{enumerate}
%{\bf Conference Proceedings:}
{\bf {Peer-reviewed Conference Publications: ($^{*}$Corresponding author)}}
\begin{enumerate}
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Profit-Maximized Task Offloading with Simulated-annealing-based Migrating Birds Optimization in Hybrid Cloud-Edge Systems," \emph{The 2020 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2020)}, Toronto, Ontario, Canada, 2020, pp. 1--6, 05/15/2020, Submitted. (\textbf{EI})
\item \textbf{Haitao Yuan} and Jing Bi, ``Fine-grained Task Scheduling in Cloud Data Centers Using Simulated-annealing-based Bees Algorithm," \emph{The 2020 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2020)}, Toronto, Ontario, Canada, 2020, pp. 1--6, 05/15/2020, Submitted. (\textbf{EI})
\item Shuang Li, Jing Bi, \textbf{Haitao Yuan} and MengChu Zhou, ``BG-LSTM: Predictive Workload and Resource for Cloud Systems," \emph{The 2020 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2020)}, Toronto, Ontario, Canada, 2020, pp. 1--6, 05/15/2020, Submitted. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``QoS and Profit Aware Task Scheduling with Simulated-Annealing-Based Bi-Objective Differential Evolution in Green Clouds," \emph{2019 IEEE 15th International Conference on Automation Science and Engineering (CASE)}, Vancouver, BC, Canada, 2019, pp. 904--909. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Spatio-Temporal Scheduling of Heterogeneous Delay-Constrained Tasks in Geo-Distributed Green Clouds," \emph{IEEE 16th International Conference on Networking, Sensing and Control (ICNSC)}, Banff, Canada, 2019, pp. 287--292. (\textbf{EI})
\item \textbf{Haitao Yuan} and Jing Bi, ``Profit-Aware Spatial Task Scheduling in Distributed Green Clouds," \emph{2019 IEEE International Conference on Systems, Man and Cybernetics (SMC 2019)}, Bari, Italy, 2019, pp. 421--426. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Revenue-sensitive Scheduling of Multi-application Tasks in Software-defined Cloud," \emph{2017 13th IEEE Conference on Automation Science and Engineering (CASE 2017)}, Xi'an, 2017, pp. 1566--1571. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Cost-sensitive Task Routing and Resource Provisioning in Geo-distributed Clouds," \emph{2017 IEEE 14th International Conference on Networking, Sensing and Control (ICNSC 2017)}, Calabria, Italy, 2017, pp. 507--512. (\textbf{EI})
\item \textbf{Haitao Yuan} and MengChu Zhou, ``Energy Cost and Performance-Sensitive Bi-objective Task Scheduling in Distributed Data Centers," \emph{IEEE 17th International Conference on Networking, Sensing and Control (ICNSC 2020)}, Nanjing, China, 2020, pp. 1--6. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi, Jia Zhang, Wei Tan and Keman Huang, ``Workload-Aware Revenue Maximization in SDN-Enabled Data Center," \emph{2017 IEEE 10th International Conference on Cloud Computing (CLOUD 2017)}, Honolulu, CA, USA, 2017, pp. 18--25. (\textbf{EI})
\item \textbf{Haitao Yuan} and Jing Bi, ``Location-Sensitive Resource Optimization for Profit Maximization in Distributed Data Centers," \emph{2019 IEEE International Conference on Systems, Man and Cybernetics (SMC 2019)}, Bari, Italy, 2019, pp. 39--44. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi, Bo Hu Li, \textit{et al}., ``SLA-based Virtualized Resource Allocation for Multi-tier Web Application in Cloud Simulation Environment," \emph{2012 IEEE International Conference on Industrial Engineering and Engineering Management (IEEM 2012)}, Hong Kong, 2012, pp. 1681--1685. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi and MengChu Zhou, ``Geographical Scheduling of Multi-application Tasks for Cost Minimization in Distributed Green Data Centers," \emph{2018 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2018)}, Miyazaki, Japan, 2018, pp. 3171--3176. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi, Xiao Song, Bo Hu Li, Tingyu Lin, Jian Zhang, and Changshun Yan, ``Revenue-Aware Request Admission Control in Distributed Simulation Data Centers," \emph{2016 International Simulation Multi-Conference (AsiaSim/SCS AutumnSim 2016)}, Beijing, China, 2016, pp. 615--623. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi, and MengChu Zhou, ``Temporal-Variation-Aware Profit-Maximized and Delay-Bounded Task Scheduling in Green Data Center," \emph{2019 International Conference on Internet and Distributed Computing Systems (IDCS 2019)}, Napoli, Italy, 2019, pp. 203--212. (\textbf{EI})
\item \textbf{Haitao Yuan}, Jing Bi, Bo Hu Li, and Xudong Chai, ``An Approach to Optimized Resource Allocation for Cloud Simulation Platform," \emph{The 14th Asia Simulation Conference \& the 33rd JSST Annual Conference: International Conference on Simulation Technology (AsiaSim \& JSST 2014)}, Beijing, China, 2014, pp. 139--152. (\textbf{EI})
\item Jing Bi, \textbf{Haitao Yuan}, Jia Zhang and MengChu Zhou, ``Temporal Task Scheduling for Delay-Constrained Applications in Geo-Distributed Cloud Data Centers," \emph{2018 IEEE 11th International Conference on Cloud Computing (CLOUD 2018)}, San Francisco, CA, USA, 2018, pp. 138--145. (\textbf{EI})
\item Jing Bi, \textbf{Haitao Yuan}, Junfei Qiao, MengChu Zhou and Xiao Song, ``Temporal Request Scheduling for Energy-efficient Cloud Data Centers," 2017 \emph{IEEE 14th International Conference on Networking, Sensing and Control (ICNSC 2017)}, Calabria, Italy, 2017, pp. 180--185. (\textbf{EI})
\item Zhiliang Zhu, \textbf{Haitao Yuan}, et al, ``WS-SCAN: An Effective Approach for Web Services Clustering," \emph{2010 International Conference on Computer Application and System Modeling}, Taiyuan, China, pp. 618--622. (\textbf{EI})
\item Jing Bi, \textbf{Haitao Yuan}, Yushun Fan, Wei Tan, and Jia Zhang, ``Dynamic Fine-Grained Resource Provisioning for Heterogeneous Applications in Virtualized Cloud Data Center," \emph{The 8th IEEE International Conference on Cloud Computing (CLOUD 2015)}, New York, USA, 2015, pp. 29--436. (\textbf{EI})
\item Libo Zhang, Jing Bi and \textbf{Haitao Yuan}, ``Workload Forecasting with Hybrid Stochastic Configuration Networks in Clouds," \emph{2018 5th IEEE International Conference on Cloud Computing and Intelligence Systems (CCIS 2018)}, Nanjing, China, 2018, pp. 112--116. (\textbf{EI})
\item Zhiliang Zhu, Jing Bi, \textbf{Haitao Yuan} and Ying Chen, ``SLA Based Dynamic Virtualized Resources Provisioning for Shared Cloud Data Centers," \emph{IEEE 4th International Conference on Cloud Computing (CLOUD 2011)}, Washington, DC, USA, 2011, pp. 630--637. (\textbf{EI})
\item Jing Bi, Libo Zhang, \textbf{Haitao Yuan} and MengChu Zhou, ``Hybrid Task Prediction Based on Wavelet Decomposition and ARIMA Model in Cloud Data Center," \emph{2018 IEEE 15th International Conference on Networking, Sensing and Control (ICNSC 2018)}, Zhuhai, China, 2018, pp. 1--6. (\textbf{EI})
\item Jing Bi, Shuang Li, \textbf{Haitao Yuan}, Z. Zhao and H. Liu, ``Deep Neural Networks for Predicting Task Time Series in Cloud Computing Systems," \emph{2019 IEEE 16th International Conference on Networking, Sensing and Control (ICNSC 2019)}, Banff, AB, Canada, 2019, pp. 86--91. (\textbf{EI})
\item Jing Bi, Zhiliang Zhu, \textbf{Haitao Yuan}, \textit{et al.}, ``A Petri Net Based Hybrid Optimal Controller for Deadlock Prevention in Web Service Composition," \emph{The 9th IEEE International Conference on Web Services (ICWS 2011)}, Washington DC, USA, 2011, pp. 718--719. (\textbf{EI})
\item Jing Bi, Zhiliang Zhu, and \textbf{Haitao Yuan}, ``SLA-Aware Dynamic Resource Provisioning for Profit Maximization in Shared Cloud Data Centers," \emph{ICHCC-ICTMF 2011}, Singapore, 2011, pp. 366--372. (\textbf{EI})
\item Quanxi Dong, Yongze Lin, Jing Bi and \textbf{Haitao Yuan}, ``An Integrated Deep Neural Network Approach for Large-Scale Water Quality Time Series Prediction," \emph{2019 IEEE International Conference on Systems, Man and Cybernetics (SMC 2019)}, Bari, Italy, 2019, pp. 3537--3542. (\textbf{EI})
\item Heng Liu, Xiaofen Zhang, Jing Bi, \textbf{Haitao Yuan} and MengChu Zhou, ``Intelligent Task Scheduling for Green Clouds with LSTM-based Prediction and Biobjective Optimization," \emph{IEEE 17th International Conference on Networking, Sensing and Control (ICNSC 2020)}, Nanjing, China, 2020, pp. 1--6. (\textbf{EI})
\item Yongze Lin, Quanxi Dong, Jing Bi, \textbf{Haitao Yuan} and MengChu Zhou, ``A Deep Learning Approach to Large-Scale Light Curve Prediction and Real-Time Anomaly Detection with Grubbs Criterion," \emph{IEEE 17th International Conference on Networking, Sensing and Control (ICNSC 2020)}, Nanjing, China, 2020, pp. 1--6. (\textbf{EI})
\item Cheng Lu, Lei Peng, Jing Bi and \textbf{Haitao Yuan}, ``An Improved Dro-Based Recurrent Neural Networks for Large-Scale Light Curve Time Series Prediction," \emph{2018 5th IEEE International Conference on Cloud Computing and Intelligence Systems (CCIS 2018)}, Nanjing, China, 2018, pp. 117--121. (\textbf{EI})
\item Hongnan Xie, Xiao Song, Jing Bi, and \textbf{Haitao Yuan}, ``VCG Auction Based Idle Instance Bidding to Increase IaaS Provider’s Profit in Hybrid Clouds," \emph{Asian Simulation Conference 2017}, Melaka, Malaysia, 2017, pp. 359--368. (\textbf{EI})
\item Xiaodong Huang, Cheng Lu, Lei Peng, Jing Bi and \textbf{Haitao Yuan}, ``A Deep Learning Approach to Large-Scale Light Curve Prediction and Real-Time Anomaly Detection with Grubbs Criterion," \emph{IEEE 17th International Conference on Networking, Sensing and Control (ICNSC 2020)}, Nanjing, China, 2020, pp. 1--6. (\textbf{EI})
\item Hang Ji, Xiao Song, Xuejun Zhang, Jing Bi, and \textbf{Haitao Yuan}, ``Internet Communication Engine (ICE) Based Simulation Framework (ISF)," \emph{2016 International Simulation Multi-Conference (AsiaSim/SCS AutumnSim 2016)}, Beijing, China, 2016, pp. 92--101. (\textbf{EI})
\item Huizhang Luo, Dan Huang, Qing Liu, Zhenbo Qiao, Hong Jiang, Jing Bi, \textbf{Haitao Yuan}, \textit{et al}., ``Identifying Latent Reduced Models to Precondition Lossy Compression," \emph{2019 IEEE International Parallel and Distributed Processing Symposium (IPDPS 2019)}, Rio de Janeiro, Brazil, 2019, pp. 293--302. (\textbf{EI})
\end{enumerate}

%\section{\sc Papers in preparation}
%
%Ventura, V., C.J. Paciorek, and J.S. Risbey.  Controlling the proportion of falsely-rejected hypotheses when conducting multiple tests with geophysical data.
%
%Ickes, K., C.J. Paciorek, and S. Thomas.  Effects of wild pigs on
%forest demographic processes in Malaysia.

%\section{\sc Conference Presentations}
%Paciorek, C.J., J.S. Risbey, V. Ventura, and R.D.Rosen.  2001.  Changes in Northern Hemisphere winter storm activity (1949-1999) based
%on a comparison of cyclone indices.  8th International Meeting on
%Statistical Climatology, Luneberg, Germany, March, 2001.
%
%Paciorek, C.J. and R. Rosenfeld.  2000.  Minimum classification error
%training in exponential language models.  2000 Spring Transcription
%Workshop, College Park, Maryland.
%\vspace*{-.25in}  
%\begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\section{\sc Services and Activities}
\begin{itemize}
	\item Technical Review Activities
	\begin{itemize}
		\item Computer Networks
		\item Computers in Industry
		\item Frontiers of Information Technology \& Electronic Engineering
		\item Future Generation Computer Systems
		\item IEEE Access
		\item IEEE/CAA Journal of Automatica Sinica
		\item IEEE Systems Journal
		\item IEEE Transactions on Automation Science and Engineering
		\item IEEE Transactions on Cloud Computing
		\item IEEE Transactions on Cybernetics
		\item IEEE Transactions on Industrial Informatics
		\item IEEE Transactions on Intelligent Transportation Systems
		\item IEEE Transactions on Parallel and Distributed Systems
		\item IETE Journal of Research
		\item International Journal of Production Research
		\item Knowledge and Information Systems
		\item KSII Transactions on Internet and Information Systems
		\item Recent Patents on Engineering
		\item Simulation Modelling Practice and Theory
		\item Swarm Intelligence
		\item The 17th IEEE International Conference on Networking, Sensing and Control (ICNSC 2020)
		\item 2020 International Conference on Intelligent Robots and Systems (IROS 2020)
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item International Conference Panel Session Chair
	\begin{itemize}
		\item The 2020 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2020), October 11--14, Toronto, Canada, 2020
		\item The 17th IEEE International Conference on Networking, Sensing and Control, June, Nanjing, China, 2020
		\item The 2016 International Simulation Multi-Conference (AsiaSim/SCS AutumnSim 2016), October 14--17, Beijing, China, 2016
		\item Asia Simulation Conference \& The International Conference on System Simulation and Scientific Computing, October 27--30, Shanghai, China, 2012
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item International Conference Technical Program Committee
	\begin{itemize}
		\item The 16th IEEE International Conference on Networking, Sensing and Control, May 9--11, Banff, Canada, 2019
		\item The 14th IEEE International Conference on Networking, Sensing and Control, May 16--18, Calabria, Southern Italy, 2017
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Professional Memberships
	\begin{itemize}
		\item IEEE, Chinese Simulation Society, China Computer Federation, IEEE Systems, Man, and Cybernetic
	\end{itemize}
\end{itemize}

\section{\sc Courses Taught}
\begin{itemize}
	\item Undergraduate Courses (\textbf{4})
	\begin{itemize}
		\item Computer Networking (in English)
		\item C++ Programming (in English)
		\item Data Structure (in Chinese)
		\item Enterprise Training (in Chinese)
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Graduate Courses (\textbf{3})
	\begin{itemize}
		\item Distributed Computing (in English)
		\item Professional English (in English)
		\item Software Project Management (in Chinese)
	\end{itemize}
\end{itemize}

\section{\sc Honors and Awards}

\begin{itemize}
	\item ``Best Paper Award-Finalist" from the 16th IEEE International Conference on Networking, Sensing and Control (IEEE ICNSC) (Top 2\%), 2019.
	\item First Prize for Scientific and Technological Progress, China Simulation Association, 2016
	\item Outstanding Graduate Student, Beihang University, 2016
	\item National Scholarship of Graduate Students (Top 5\%), Beihang University, 2015
	\item Full Tuition Scholarship for Two Years' Study, 2010-2012.
	\item Outstanding Graduate Student, Northeastern University, 2012
	\item Google Excellence Scholarship, 2011
\end{itemize}

%``Best Paper Award-Finalist" from the 16th IEEE International Conference on Networking, Sensing and Control (IEEE ICNSC) (Top 2\%), 2019.
%
%\vspace*{-2.5mm}
%First Prize for Scientific and Technological Progress, China Simulation Association, 2016
%
%\vspace*{-2.5mm}
%Outstanding Graduate Student, Beihang University, 2016
%
%\vspace*{-2.5mm}
%National Scholarship of Graduate Students (Top 5\%), Beihang University, 2015
%
%\vspace*{-2.5mm}
%Full Tuition Scholarship for Two Years' Study, 2010-2012.
%
%\vspace*{-2.5mm}
%Outstanding Graduate Student, Northeastern University, 2012
%
%\vspace*{-2.5mm}
%Google Excellence Scholarship, 2011

% \begin{itemize}
%	\item  First Level
%	\begin{itemize}
%		\item  Second Level
%		\begin{itemize}
%			\item  Third Level
%			\begin{itemize}
%				\item  Fourth Level
%			\end{itemize}
%		\end{itemize}
%	\end{itemize}
%\end{itemize}

%\section{\sc Professional Activities}
%{\bf Bureau of Transportation Statistics, U.S. Department of
%Transportation}, Washington, District of Columbia USA
%
%\vspace{-.3cm}
%{\em Summer researcher} \hfill {\bf May, 2000 - August, 2000}\\
%Carried out several consulting projects, including modelling of
%injuries to cadavers in crash test experiments, analysis of airline
%delay data, and advice on analysis of airline economics data.
%
%{\bf Abt Associates}, Bethesda, Maryland USA
%
%\vspace{-.3cm}
%{\em Associate Programmer Analyst and Research Assistant} \hfill {\bf
%October, 1994 - August, 1996}\\
%Researcher and computer model developer for U.S. EPA Regulatory Impact
%Analysis of Section 403 Lead Paint Hazard Rule.  Other projects
%included database analysis, literature reviews, and cost-benefit analysis.


%\section{\sc Computer Skills} 
%\begin{list2}
%\item Statistical Packages:  R, S-Plus, BUGS; some experience
%with SAS; extensive use of C and Fortran statistical libraries.
%\item Languages:  C++, Perl, Pascal, some use of Unix shell scripts,
%MPI parallel processing library.
%\item Applications: Generic Mapping Tools (GMT) - Unix mapping software, \LaTeX, common Windows
%database, spreadsheet, and presentation software
%\item Algorithms: Experience programming Markov Chain Monte Carlo
%simulations of Bayesian posterior distributions
%\item Operating Systems:  Unix/Linux, Windows.\\ 
%\end{list2}



\end{resume}
\end{document}




